--- 
title: "README" 
author: "Peter Meißner" 
date: "`r Sys.Date()`" 
output: html_document 
---


# Testing the programming properties of hellno

R's default behaviour in regard to creating data.frames is to convert any
charcter vectors to type factor - some like it, some not ... 

```{r} 
data.frame(a=letters[1:2])$a 
```

Now the hellno package was written to overcome that feature in case one does not 
at all like the default and prefers to be explicit about string conversion and 
one stil wants to use data.frames. Loading the package will result in 
putting the alternative implementations of `data.frame()` and `as.data.frame()`
before those from package base. R gives a message to inform us about that and 
hence the no string conversion takes place anymore:

```{r} 
library(hellno)
data.frame(a=letters[1:2])$a 
```

Unloading hellno again to show programming behaviour: 

```{r}
unloadNamespace("hellno")
```

Another approach is to use hellno as import in other packages to get the behaviour 
consistently inside a package. 

Loading the package (that uses hellno internally) does not change the default R 
behaviour.

```{r}
library(hellnotests)
data.frame(a=letters[1:2])$a 
```

While all functions within the package use hellno's alternative implementations:

```{r}
hellno_df
```

... and hence for them string conversion is no matter anymore:

```{r}
hellno_df()
```





